Python as a machine learning language: experiences from the \textit{scikit-learn} project

### 2013-06-08 paper.tex
typo

Within the past few years, the project has proved valuable to an ever
increasing user base. Its popularity can be gaged from various indicators
such as hundreds of citations in scientific papers, successes in various
machine learning challenges (\emph{e.g.} kaggle), or significant
statistics\footnote{As of writing, 1309 stars and 667 forks of the
project on github, 300 mails per months on the user mailing list, 385
questions tagged \emph{scikit-learn} on {\tt stackoverflow}} derived from
our repositories and mailing lists.

>>>>

Within the past few years, the project has proved valuable to an ever
increasing user base. Its popularity can be gaged from various indicators
such as hundreds of citations in scientific papers, successes in various
machine learning challenges (\emph{e.g.} kaggle), or significant
statistics\footnote{As of writing, 1309 stars and 667 forks of the
project on github, 300 mails per months on the user mailing list, 385
questions tagged \emph{scikit-learn} on {\tt stackoverflow}.} derived from
our repositories and mailing lists.
